---
title: "Step1_Plumas"
author: "Christina Fossum"
date: "2023-09-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Extracting data from .nc to .csv format

This document contains code and explanation for extracting the DRI weather data in raster form from CalFire external harddrive into workable .csv file. This is the first step in processing/analysing this data for prescribed burn window analysis


# 1. Load shapefile for county of interest (in this case, Plumas), and function to process weather data

```{r}

library(here)
library(tidyverse)
library(raster)
library(sf)
library(sp)
library(rgdal)
library(data.table)

plumas <- read_sf("california_counties/CaliforniaCounties.shp")
plumas <- plumas %>% filter(NAME=="Plumas")
plumas <- plumas %>% dplyr::select(NAME, geometry)
plumas <- st_transform(plumas, crs=26910)


fun <- function(x){  
  zz1 <- brick(x)
  zzlat <- brick(x, varname="XLAT")
  zzlon <- brick(x, varname="XLONG")
  latm <- as.matrix(zzlat)
  lonm <- as.matrix(zzlon)
  LL <- cbind(latm, lonm)
  colnames(LL) <- c("Lat", "Long")
  LL <- as_tibble(LL)
  matrix <- as.matrix(zz1)
  matrix <- as.tibble(matrix)
  all <- cbind(LL, matrix)
  coordinates(all) <- c("Long", "Lat")
  proj4string(all) <- CRS("+proj=longlat +datum=WGS84")
  res <- spTransform(all, CRS("+proj=utm +zone=10"))
  all.sf <- st_as_sf(res, coords = c('Long', 'Lat'), crs = st_crs(plumas))
  all.sf <- st_transform(all.sf, crs=26910)
  i1 <- st_intersection(all.sf, plumas)
}



```

# 2. Load monthly data for each year / extract / save
Instructions: do 1 month at a time through to writing the .csv file
Note- will probably need to clear memory and/or restart R every couple of years
Note- below I only have 2016-2018 for RH. Use whatever your file path is for other years and do the same for temp and wind

```{r}
jan16 <- "RH/WRFV1_RH_SFC2016/WRF_RH_SFC_01_2016.nc"
feb16<- "RH/WRFV1_RH_SFC2016/WRF_RH_SFC_02_2016.nc"
mar16<- "RH/WRFV1_RH_SFC2016/WRF_RH_SFC_02_2016.nc"
apr16<- "RH/WRFV1_RH_SFC2016/WRF_RH_SFC_04_2016.nc"
may16<- "RH/WRFV1_RH_SFC2016/WRF_RH_SFC_05_2016.nc"
jun16<- "RH/WRFV1_RH_SFC2016/WRF_RH_SFC_06_2016.nc"
jul16<- "RH/WRFV1_RH_SFC2016/WRF_RH_SFC_07_2016.nc"
aug16<- "RH/WRFV1_RH_SFC2016/WRF_RH_SFC_08_2016.nc"
sep16<- "RH/WRFV1_RH_SFC2016/WRF_RH_SFC_09_2016.nc"
oct16<- "RH/WRFV1_RH_SFC2016/WRF_RH_SFC_10_2016.nc"
nov16<- "RH/WRFV1_RH_SFC2016/WRF_RH_SFC_11_2016.nc"
dec16<- "RH/WRFV1_RH_SFC2016/WRF_RH_SFC_12_2016.nc"
month16 <- c(jan16, feb16, mar16, apr16, may16, jun16, jul16, aug16, sep16, oct16, nov16, dec16)

list16 <- lapply(month16, fun)
data16 <- (do.call(cbind, list16))

fwrite(data16, "Routput/Plumas/plumas_rh_2016.csv")

~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

jan17 <- "RH/WRFV1_RH_SFC2017/WRF_RH_SFC_01_2017.nc"
feb17<- "RH/WRFV1_RH_SFC2017/WRF_RH_SFC_02_2017.nc"
mar17<- "RH/WRFV1_RH_SFC2017/WRF_RH_SFC_02_2017.nc"
apr17<- "RH/WRFV1_RH_SFC2017/WRF_RH_SFC_04_2017.nc"
may17<- "RH/WRFV1_RH_SFC2017/WRF_RH_SFC_05_2017.nc"
jun17<- "RH/WRFV1_RH_SFC2017/WRF_RH_SFC_06_2017.nc"
jul17<- "RH/WRFV1_RH_SFC2017/WRF_RH_SFC_07_2017.nc"
aug17<- "RH/WRFV1_RH_SFC2017/WRF_RH_SFC_08_2017.nc"
sep17<- "RH/WRFV1_RH_SFC2017/WRF_RH_SFC_09_2017.nc"
oct17<- "RH/WRFV1_RH_SFC2017/WRF_RH_SFC_10_2017.nc"
nov17<- "RH/WRFV1_RH_SFC2017/WRF_RH_SFC_11_2017.nc"
dec17<- "RH/WRFV1_RH_SFC2017/WRF_RH_SFC_12_2017.nc"
month17 <- c(jan17, feb17, mar17, apr17, may17, jun17, jul17, aug17, sep17, oct17, nov17, dec17)

list17 <- lapply(month17, fun)
data17 <- (do.call(cbind, list17))

fwrite(data17, "Routput/Plumas/plumas_rh_2017.csv")

~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

jan18 <- "RH/WRFV1_RH_SFC2018/WRF_RH_SFC_01_2018.nc"
feb18<- "RH/WRFV1_RH_SFC2018/WRF_RH_SFC_02_2018.nc"
mar18<- "RH/WRFV1_RH_SFC2018/WRF_RH_SFC_02_2018.nc"
apr18<- "RH/WRFV1_RH_SFC2018/WRF_RH_SFC_04_2018.nc"
may18<- "RH/WRFV1_RH_SFC2018/WRF_RH_SFC_05_2018.nc"
jun18<- "RH/WRFV1_RH_SFC2018/WRF_RH_SFC_06_2018.nc"
jul18<- "RH/WRFV1_RH_SFC2018/WRF_RH_SFC_07_2018.nc"
aug18<- "RH/WRFV1_RH_SFC2018/WRF_RH_SFC_08_2018.nc"
sep18<- "RH/WRFV1_RH_SFC2018/WRF_RH_SFC_09_2018.nc"
oct18<- "RH/WRFV1_RH_SFC2018/WRF_RH_SFC_10_2018.nc"
nov18<- "RH/WRFV1_RH_SFC2018/WRF_RH_SFC_11_2018.nc"
dec18<- "RH/WRFV1_RH_SFC2018/WRF_RH_SFC_12_2018.nc"
month18 <- c(jan18, feb18, mar18, apr18, may18, jun18, jul18, aug18, sep18, oct18, nov18, dec18)

list18 <- lapply(month18, fun)
data18 <- (do.call(cbind, list18))

fwrite(data18, "Routput/Plumas/plumas_rh_2018.csv")

```

# 3. Load annual 100hr fuel moisture data / extract / save

```{r}

y2003 <- "fm100/fm100_2003.nc"
y2004 <- "fm100/fm100_2004.nc"
y2005 <- "fm100/fm100_2005.nc"
y2006 <- "fm100/fm100_2006.nc"
y2007 <- "fm100/fm100_2007.nc"
y2008 <- "fm100/fm100_2008.nc"
y2009 <- "fm100/fm100_2009.nc"
y2010 <- "fm100/fm100_2010.nc"
y2011 <- "fm100/fm100_2011.nc"
y2012 <- "fm100/fm100_2012.nc"
y2013 <- "fm100/fm100_2013.nc"
y2014 <- "fm100/fm100_2014.nc"
y2015 <- "fm100/fm100_2015.nc"
y2016 <- "fm100/fm100_2016.nc"
y2017 <- "fm100/fm100_2017.nc"
y2018 <- "fm100/fm100_2018.nc"

year <- c(y2003, y2004, y2005, y2006, y2007, y2008,
          y2009, y2010, y2011, y2012, y2013, y2014, y2015, y2016, y2017, y2018)

list <- lapply(year, fun)

data <- do.call(cbind, list)
fwrite(data, "Routput/fm_plumas.csv")

```

END.
